Blas\'e3D

### 2023-11-09 paper/paper2/ms.tex
Table things

\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{bm}
\usepackage{enumitem}
% Temporary packages
\usepackage{mdframed}
\usepackage{verbatim}

@@

>>>>

\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{graphicx}
% Temporary packages
\usepackage{mdframed}
\usepackage{verbatim}

@@

Here is a table of the performance of different manifold choices:

\begin{deluxetable*}{cccc}[h]
    \tabletypesize{\small}
    \tablecaption{Notation used in this paper\label{table2}}
    \tablehead{
        \colhead{Model Architecture} & \colhead{Reconstruction RMS} & \colhead{Model Size} & \colhead{Training Time}
        \\\colhead{} & \colhead{RMS \%} & \colhead{MB} & \colhead{x} 
        }
    \startdata
    Linear Polynomial & a & b & c\\
    FFT & a & b & c\\
    Random Forest & a & b & c\\
    Gaussian Process & a & b & c\\
    Interpolation & a & b & c\\
    Interpolation & a & b & c\\ 
    \enddata
\end{deluxetable*}
